Computer Science House Constitution

### 2025-09-22 constitution.tex
Added in the Squatters Rights Clause

Active Members currently on co-op forfeit their right to vote on house issues, and likewise do not count towards quorum.
Exceptions may be made at the discretion of the Evaluations Director.

@@

\asubsection{Honorary and Advisory Membership Selection}
\begin{enumerate}
	\item A CSH member submits a nomination to the Evals Director, in writing, for a person they feel is deserving of Honorary or Advisory Membership. The nomination must specify the type of membership the nominee is nominated for.
	\item The Evals Director performs preliminary research on the candidate and presents the findings.
	\item If E-Board decides not to present the nomination at a House Meeting, the selection process ends and the candidate does not become a member.
	\item If the nomination is presented at a House Meeting for discussion, a Two-Thirds Vote with two-thirds quorum is held to determine whether the nomination is accepted.
	      Ballots are distributed and voting must remain open for a minimum of a forty-eight hour period.
	\item Candidates selected for Honorary Membership are notified of their selection as an Honorary Member and presented with the honor.
	\item Candidates selected for Advisory Membership are notified of their acceptance as CSH Advisors and asked to accept or decline the selection.
\end{enumerate}

\asubsection{Honorary and Advisory Membership Expectations}
There are no expectations associated with the Honorary or Advisory Membership status.

@@

\asubsection{Housing Priority System}
The Housing Priority System is a means for determining the priority a member has in a housing issue or the assignment of available housing.
The member with top priority is the member with On-Floor Status and the most Housing Priority Points.
Housing Priority Points are accumulated once per Operating Session at the conclusion of the Membership Eval.
Each Active Member who passes the Membership Eval is granted two Housing Priority Points.

>>>>

@@

\asubsection{Honorary and Advisory Membership Selection}
\begin{enumerate}
	\item A CSH member submits a nomination to the Evals Director, in writing, for a person they feel is deserving of Honorary or Advisory Membership. The nomination must specify the type of membership the nominee is nominated for.
	\item The Evals Director performs preliminary research on the candidate and presents the findings.
	\item If E-Board decides not to present the nomination at a House Meeting, the selection process ends and the candidate does not become a member.
	\item If the nomination is presented at a House Meeting for discussion. A Two-Thirds Vote with two-thirds quorum is held to determine whether the nomination is accepted.
	      Ballots are distributed and voting must remain open for a minimum of a forty-eight hour period.
	\item Candidates selected for Honorary Membership are notified of their selection as an Honorary Member and presented with the honor.
	\item Candidates selected for Advisory Membership are notified of their acceptance as CSH Advisors and asked to accept or decline the selection.
\end{enumerate}

\asubsection{Honorary Membership Expectations}
There are no expectations associated with the Honorary Membership status.

\asubsection{Advisory Membership Expectations}
There are no expectations associated with the Advisory Membership status.

@@

\asubsection{Housing Priority System}
The Housing Priority System is a means for determining the priority a member has in a housing issue or the assignment of available housing.
The member with top priority is the member with On-Floor Status and the most Housing Priority Points.
Housing Priority Points are accumulated once per Operating Session at the conclusion of the Membership Eval.
Each Active Member who passes the Membership Eval is granted two Housing Priority Points. 
Members registered with NTID receive priority over members with equivalent Housing Priority points. % NTID students can ONLY choose dorms with doorbells, so this helps ensure that students who need these rooms have access to them. 
Members who require accommodations may be temporarily granted additional Housing Priority Points at the request of RIT Housing or at the discretion of the Evaluations Director. 
Temporary Housing Priority Points remain in effect until the end of the Standard Operating Session or an earlier date, as specified when granted.
Additionally, members are granted 0.5 Temporary Housing Priority Points for the duration of time that they are assigned to the room they currently live in.
